\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Fix typo

Regarding future work, the next logical steps would be to repeat this analysis in other TLDs, and to improve the homograph matching algorithm.
A more challenging enchancement would be to perform the classification of homograph IDNs without manual intervention by analyzing \textit{WHOIS} records and the \textit{HTTP/HTML} responses.

>>>>

Regarding future work, the next logical steps would be to repeat this analysis in other TLDs, and to improve the homograph matching algorithm.
A more challenging enhancement would be to perform the classification of homograph IDNs without manual intervention by analyzing \textit{WHOIS} records and the \textit{HTTP/HTML} responses.
